\sysfull

### 2018-04-17 paper/evaluation.tex
correct the algo names

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalEfficiency}
    \caption{Breakdown of overhead for the proposed coalescing strategies
relative to the baseline without coalescing.
NC: no coalescing, EB: energy-blind coalescing, HG: history-guided coalescing, WHG:
energy- and task-aware coalescing. All coalescing strategies reduce total
overhead and maximize useful work. HG and WHG perform better than EB.}
	\label{fig:overallOverheadBreakdown}
	%\end{figure}
\end{wrapfigure}

@@

For each coalescing strategy from Section~\ref{sec:task_adaptation} (EB, HG,
and WHG) and for a baseline without coalescing (NC), we have measured the time
spent on (i) executing useful task code, including \sys's overhead on access to
protected variables, (ii) re-executing task code after a power failure, and
(iii) committing state to non-volatile memory at the end of each (coalesced)
task.  In this experiment the WISP was 15\,cm away from the signal generator
antenna.
%
The page size was set to the best performing value (32~B for \textbf{bc} and
256~B pages for the rest) identified in detailed evaluation of paging in
Section~\ref{sec:results_memory_management}.

The overhead incurred by each coalescing strategy is broken down in
Figure~\ref{fig:overallOverheadBreakdown}. Without coalescing enabled (NC), the
re-execution penalty is smallest, because the amount of work that can happen
between commits and may have to be re-executed if interrupted is smallest when
work from multiple static tasks is not combined.
%
However, any gain from a reduced re-execution penalty is cancelled out by
the increased commit overhead that is incurred at the end of each static
task.
%
Across all benchmarks, all coalescing strategies reduce more commit overhead
than the re-execution overhead they add.
%
This net overhead reduction is greatest in HG and WHG strategies compared
to the EB strategy. We attribute this discrepancy to EB's slow adjustment
of the target task size without regard to execution history.
%
In the subsequent experiments, we focus on the better-performing HG and WHG
strategies.

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
	%\begin{figure}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coalEfficiency}
    \caption{Breakdown of overhead for the proposed coalescing strategies
relative to the baseline without coalescing.
NC: no coalescing, EO: energy-blind coalescing, HG: history-guided coalescing, WHG:
energy- and task-aware coalescing. All coalescing strategies reduce total
overhead and maximize useful work. HG and WHG perform better than EO.}
	\label{fig:overallOverheadBreakdown}
	%\end{figure}
\end{wrapfigure}

@@

For each coalescing strategy from Section~\ref{sec:task_adaptation} (EO, HG,
and WHG) and for a baseline without coalescing (NC), we have measured the time
spent on (i) executing useful task code, including \sys's overhead on access to
protected variables, (ii) re-executing task code after a power failure, and
(iii) committing state to non-volatile memory at the end of each (coalesced)
task.  In this experiment the WISP was 15\,cm away from the signal generator
antenna.
%
The page size was set to the best performing value (32~B for \textbf{bc} and
256~B pages for the rest) identified in detailed evaluation of paging in
Section~\ref{sec:results_memory_management}.

The overhead incurred by each coalescing strategy is broken down in
Figure~\ref{fig:overallOverheadBreakdown}. Without coalescing enabled (NC), the
re-execution penalty is smallest, because the amount of work that can happen
between commits and may have to be re-executed if interrupted is smallest when
work from multiple static tasks is not combined.
%
However, any gain from a reduced re-execution penalty is cancelled out by
the increased commit overhead that is incurred at the end of each static
task.
%
Across all benchmarks, all coalescing strategies reduce more commit overhead
than the re-execution overhead they add.
%
This net overhead reduction is greatest in HG and WHG strategies compared
to the EO strategy. We attribute this discrepancy to EO's slow adjustment
of the target task size without regard to execution history.
%
In the subsequent experiments, we focus on the better-performing HG and WHG
strategies.
